---
title: "Sp23_Mulla_Assignment_02"
author: "Areej Mulla"
date: "2/16/2023"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r read_data}
library(readr)
SuperStoreOrders <- read_csv(paste0(getwd(), "/Project02_SuperStoreOrders.csv"))
```
**Question 1** <br>
The data set illustrates no missing values and includes 51290 records.
sales, quantity, discount, profit, shipping_cost, order_priority and
year are all numeric variables, while the rest are character variables.
```{r summarize_data}
summary(SuperStoreOrders)
```

```{r}
library(ggplot2)
```

**Question 2** <br>
The number of orders for each of the segments is increasing over the years,
with the consumer segment illustrating the largest number of
orders in each year.
```{r order_by_segment}
layer1 <- ggplot(data = SuperStoreOrders)
layer1 +
  geom_bar(aes(x = year , fill = segment)) +
  xlab("Year of Order")
```

**Question 3** <br>
The bar chart below illustrates that the consumer segment is the best seller.
```{r}
library(dplyr) 
SuperStoreOrders %>% 
  mutate(total_sales = sum(sales)) %>%
  group_by(segment) %>%
  summarize(total_sales = sum(sales)) %>%
ggplot() +
  geom_bar(aes(x = segment, y = total_sales), stat = "identity") +
  scale_x_discrete(name = "Segment") 
```
**Question 4** <br>
The bar chart below illustrates that the Central region receives
the most orders, while the region of Canada receives the fewest orders.
```{r regional_orders}
layer1 + 
  geom_bar(mapping = aes(x = reorder(region, region, 
                                     FUN = function(x) length(x))), 
                         fill = "blue")+
  coord_flip() +
   scale_x_discrete(name = "Region")
```
**Question 5** <br>
```{r}
SuperStoreOrders %>% 
  mutate(total_profit = sum(profit)) %>%
  group_by(region) %>%
  summarize(total_profit = sum(profit)) %>%
  ggplot() +  geom_bar(mapping = aes(x = region, y = total_profit,
                                     fill = region),
                                      stat = "identity") +
  coord_polar() + scale_y_continuous(labels = scales::comma_format()) 
```
**Question 6** <br>
The density plot below illustrates a net positive profit.
```{r}
layer1 +
  geom_density(aes(x = profit)) + 
  scale_x_continuous(limits = c(-125, 125))

```



**Honors Pledge:**

**As a student of the Dr. Robert B. Pamplin Jr. School of Business I have read and strive to uphold the University’s Code of Academic Integrity and promote ethical behavior. In doing so, I pledge on my honor that I have not given, received, or used any unauthorized materials or assistance on this examination or assignment.  I further pledge that I have not engaged in cheating, forgery, or plagiarism and I have cited all appropriate sources.**

Student Signature: Areej Mulla


