---
title: "Sp23_Midterm_Exam"
author: "Areej Mulla"
date: "3/2/2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reading the File
```{r bank_full}
library(readr)
bank_full <- read_delim(paste0(getwd(), "/bank_full.csv"))
```

## Cleaning the Data

The data set has no NA values, but rather has "unknown" values.

### Addressing the Dependent Variable (y):
```{r dependent_var}
# convert the dependent variable to 0s & 1s
bank_full$y <- ifelse(bank_full$y == "yes", 1, 0)
```

### Addressing the Independent Variables:
```{r independent_var}

# treat "education" as a factor from 1 to 4 (has "unknown" values)
bank_full$education <- factor(bank_full$education,
                            level = c("unknown", "primary", "secondary", "tertiary"),
                            exclude = NULL)

bank_full$housing <- ifelse(bank_full$housing == "yes", 1, 0)
bank_full$loan <- ifelse(bank_full$loan == "yes", 1, 0)
bank_full$default <- ifelse(bank_full$default == "yes", 1, 0)

# treat "contact" as a factor from 1 to 3 (has "unknown" values)
bank_full$contact <- factor(bank_full$contact,
                            level = c("unknown", "cellular", "telephone"),
                            exclude = NULL)

# treat marital as a factor from 1 to 3 (doesn't have "unknown" values)
bank_full$marital <- factor(bank_full$marital,
                            level = c("single", "divorced", "married"),
                            exclude = NULL)

# treat job as a factor from 1 to 12 (has "unknown" values)
bank_full$job <- factor(bank_full$job,
                            level = c("unknown", "unemployed", "student",
                                      "housemaid", "services", "blue-collar",
                                      "retired", "admin.", "self-employed",
                                      "technician", "management", "entrepreneur"),
                            exclude = NULL)

# treat poutcome as a factor from 1 to 4 (has "unknown" values)
bank_full$poutcome <- factor(bank_full$poutcome,
                            level = c("unknown", "failure", "other", "success"),
                            exclude = NULL)

# normalizing "balance" to handle dispersion 
bank_full$balance <- (bank_full$balance - mean(bank_full$balance)) / sd(bank_full$balance)
```


## Creating a Training Sample to fit the Model & a Test Sample to Test the Model
```{r train_test_samples}
set.seed(100)
bank_full$test_train_indicator <- sample(c("Train", "Test"),
                               nrow(bank_full),
                               replace = T,
                               prob = c(0.8, 0.2))

train <- bank_full[bank_full$test_train_indicator == "Train", ]
test <- bank_full[bank_full$test_train_indicator == "Test", ]
```

## Running a Logistic Regression Model on the Training Data
```{r train_glm}

glmModel <- glm(y ~ ., data = train[c(-10, -11, -12, -18)] , family = "binomial")
summary(glmModel)

# predict the data to identify the accuracy of the training sample
outcome <- predict(glmModel, train[c(-10, -11, -12, -18)], "response")
outcome <- ifelse(outcome > 0.5, 1, 0)

# add the outcome to training sample
train$outcome <- outcome

# create a confusion matrix
confusionMatrix <- as.data.frame(table(train$outcome, train$y))
names(confusionMatrix) <- c("prediction", "True_value", "Count")
confusionMatrix 

# identify the accuracy of the training model
accuracy <- sum(confusionMatrix[confusionMatrix$prediction == confusionMatrix$True_value, "Count"]) / sum(confusionMatrix$Count)
accuracy

```

## Running a Logistic Regression Model on the Test Data
```{r test_glm}

# predict the data to see the accuracy of the test sample
glmModel2 <- glm(y ~ ., data = test[c(-10, -11, -12, -18)] , family = "binomial")
summary(glmModel2)

# predict the data to identify the accuracy of the test sample
outcome <- predict(glmModel2, test[c(-10, -11, -12, -18)], "response")
outcome <- ifelse(outcome > 0.5, 1, 0)

# add the outcome to test sample
test$outcome <- outcome

# create a confusion matrix
confusionMatrix <- as.data.frame(table(test$outcome, test$y))
names(confusionMatrix) <- c("prediction", "True_value", "Count")
confusionMatrix 

# identify the accuracy of the test model
accuracy <- sum(confusionMatrix[confusionMatrix$prediction == confusionMatrix$True_value, "Count"]) / sum(confusionMatrix$Count)
  accuracy
```
## Creating a Heat Map as a Tile Plot
```{r tile_plot}
# heat..
library(ggplot2)
ggplot(data = confusionMatrix) +
  geom_tile(aes(x = prediction, y = True_value), fill = c("green", "red", "red", "green")) +
  geom_text(aes(x = prediction, y = True_value, label = Count))

```




## Conclusion
- The training sample demonstrates around 89.34% accuracy
- The test sample demonstrates 89.21% accuracy
- The number of correct classifications (32384) > the number of incorrect classifications (3864)


**Honors Pledge:**

**As a student of the Dr. Robert B. Pamplin Jr. School of Business I have read and strive to uphold the University’s Code of Academic Integrity and promote ethical behavior. In doing so, I pledge on my honor that I have not given, received, or used any unauthorized materials or assistance on this examination or assignment.  I further pledge that I have not engaged in cheating, forgery, or plagiarism and I have cited all appropriate sources.**

Student Signature: Areej Mulla
