---
title: "Sp23_Midterm_Exam"
author: "Areej Mulla"
date: "3/2/2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1: Reading the File & Printing the Summary
```{r housing_prices}
library(readr)
housing_prices <- read_csv(paste0(getwd(), "/melbourne_housing_prices.csv"))
summary(housing_prices)
```

## Question 2: Computing the Sum of Missing Records for Each Column

The summary demonstrates that the following columns having missing values:

- "Car" = 62 missing values

- "BuildingArea" = 6450 missing values

- "YearBuilt" = 5375 missing values

- "CouncilArea" = 1369 missing values

Below is the analysis on whether it is acceptable to eliminate the missing values
and the reasoning:

- "Car": 62 records is not a significant number compared to the total number of
records of 13580, and thus the corresponding entries can be eliminated.

- "CouncilArea" does not include a significant number of missing values, and
thus the corresponding entries can be eliminated. 

- "BuildingArea" and "YearBuilt" have a significant number of missing values
and are crucial indicators of a house price, and thus the corresponding entries
should not be eliminated, but rather should be imputed. 

## Question 3: Creating a Histogram to Illustrate Price Distribution
```{r layer1}
library(ggplot2)
layer1 <- ggplot( data = housing_prices)
```

### Plot #1:
```{r histogram}
layer1 + 
  geom_histogram(aes(x=Price)) + 
  scale_x_continuous(labels = scales::dollar_format())
```

### Plot #2 (With log10 Scale):
```{r histogram_log10_scale}
layer1 + 
  geom_histogram(aes(x=Price)) + 
    scale_x_log10(labels = scales::dollar_format())
```

## Question 4: Creating a Facet Histogram

### Plot #1:
```{r facet_histogram_plot}
ggplot(housing_prices[!is.na(housing_prices$Price),]) +
  geom_histogram(aes(x = Price)) + 
  scale_x_log10(labels = scales::dollar_format(), name = "Price") +
  facet_wrap(~Rooms) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  ylab("Number of Houses")

```

### Plot #2 (With free_y):
```{r facet_histogram_plot_free_y}
ggplot(housing_prices[!is.na(housing_prices$Price),]) +
  geom_histogram(aes(x = Price)) + 
  scale_x_log10(labels = scales::dollar_format(), name = "Price")+
  facet_wrap(~Rooms, scale = "free_y") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  ylab("Number of Houses")
```

## Question 5: Creating a Correlation Matrix
```{r correlation_matrix}
options(digits = 2)
numeric_column_names <- unlist(sapply(housing_prices, is.numeric))
cor_matrix <- cor(housing_prices[,numeric_column_names], use="pairwise.complete.obs")
knitr::kable(cor_matrix)
```

**Honors Pledge:**

**As a student of the Dr. Robert B. Pamplin Jr. School of Business I have read and strive to uphold the University’s Code of Academic Integrity and promote ethical behavior. In doing so, I pledge on my honor that I have not given, received, or used any unauthorized materials or assistance on this examination or assignment.  I further pledge that I have not engaged in cheating, forgery, or plagiarism and I have cited all appropriate sources.**

Student Signature: Areej Mulla